Corpus

### 2020-05-15 evaluation/R/corpus.Rmd
Add revdeps code coverage into corpus

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_metadata, by="package") %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_coverage_funs, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_classes, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```

>>>>

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_metadata, by="package") %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_coverage_funs, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_classes, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_revdeps_coverage, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```
